Union and intersection contracts are hard, actually

### 2021-06-10 paper.tex
Typo
Remove unnecessary paragraph

Although sound, this interpretation is weaker than what the
coinductive semantics permit. Consider the two contexts presented on
Figure~\ref{fig:valid-contexts}. The first one is a context satisfying
\nickel{Num -> Num}, applying the hole to a number. Similarly, the second context
from the same figure satisfies \nickel{Bool -> Bool}.

@@

The implementation of casts relies on abstract interpretation, leading to a
complex specification, whose implementation is not straightforward. It is not clear
either how much these casts rely on static type information to function
correctly, possibly hampering their transformation to more general standalone
contracts.

>>>>

Although sound, this interpretation is weaker than what the
coinductive semantics permits. Consider the two contexts presented on
Figure~\ref{fig:valid-contexts}. The first one is a context satisfying
\nickel{Num -> Num}, applying the hole to a number. Similarly, the second context
from the same figure satisfies \nickel{Bool -> Bool}.

@@
